---
title: "simpleRegress"
author: "Amia Little"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```
for model length~neck, adjusted r^2 = 0.75

## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

## length based on age


```{r}
simp <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(simp)
summary.lm(simp)
```
adjusted $r^2$ for age model is 0.51, this is less than the adjusted $r^2$ for neck , so this model is not as good as the neck model. 

```{r}
chestModel<- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(chestModel)
summary.lm(chestModel)
```

adjusted $r^2$ for chest length is 0.78, this is greater than the adjusted $r^2$ for neck and age so this model is better than neck and age model.

 

```{r}
simp <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```
adjusted $r^2$ for headwth is 0.53, this is less than adjusted $r^2$ for neck,age,and chest so this model is not greater than neck,age,or chest models.


```{r}
simp <- lm(LENGTH~SEX,data=bears)
plot(LENGTH~SEX,data=bears)

summary.lm(simp)
```

adjusted $r^2$ for sex is 0.00, this is less than the adjusted $r^2$ of neck, headwth,chest,and age models.

```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)

summary.lm(simp)
```

adjusted $r^2$ is 0.74, the adjusted $r^2$ is less than neck, chest, and weight models but less than sex model.

```{r}
simp <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)

summary.lm(simp)
```

adjusted $r^2$ for headlen is 0.84 which is greater than all model so it is the best model.

```{r}
simp <- lm(WEIGHT~LENGTH,data=bears)
plot(WEIGHT~LENGTH,data=bears)

summary.lm(simp)
```
adjusted $r^2$ of length is 0.74, that is greater than neck.         